---
title: "p8105_hw1_sl5685"
author: "Shumei Liu"
date: "2024-09-21"
output: github_document
---

## Problem 1
```{r}
data("penguins", package = "palmerpenguins")
```

The dataset contains information on species, island, bill length (mm), bill depth (mm), flipper length (mm), body mass (g), sex and year for different penguin species.

* species: The penguin species.
* island: The island where the penguins were observed.
* bill_length_mm: The length of the penguins' bill (in mm).
* bill_depth_mm: The bill depth (in mm)  
* flipper_length_mm: The length of the penguins' flipper (in mm).
* body_mass_g: The body mass of the penguins (in grams).
* sex: The sex of the penguin.

The dataset has `r nrow(penguins)` rows and `r ncol(penguins)` columns. 
The mean flipper length is `r mean(penguins$flipper_length_mm, na.rm = TRUE)` mm.

```{r}
library(tidyverse)

ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) +
  geom_point()

ggsave("penguins_plot.pdf", height = 4, width = 10)
```

## Problem 2

#### Data frame
```{r}
df <- data.frame(
  numeric_var = rnorm(10),  # Random sample from standard normal distribution
  logical_var = rnorm(10) > 0,  # Logical vector
  char_var = letters[1:10],  # Character vector
  factor_var = factor(rep(c("a", "b", "c"), length.out = 10))  # Factor vector
)
df
```

#### Mean
```{r}
mean_numeric <- mean(df %>% pull(numeric_var))  # This works
mean_numeric

mean_logical <- mean(df %>% pull(logical_var))  # This works
mean_logical

# mean_char <- mean(df %>% pull(char_var))  # Not work

# mean_factor <- mean(df %>% pull(factor_var))  # Not work 
```

```{r}
numeric_logical <- as.numeric(df$logical_var) 
mean_numeric_logical <- mean(numeric_logical)
```
```{r}
numeric_char <- as.numeric(df$char_var) 
mean_numeric_char <- mean(numeric_char)# Not work
```
```{r}
numeric_factor <- as.numeric(df$factor_var)
mean_numeric_factor <- mean(numeric_factor)
```
* Numeric variable: The mean is calculated directly.
* Logical variable: TRUE is treated as 1 and FALSE as 0, so the mean is calculated as the proportion of TRUE values.
* Character variable: Cannot calculate the mean due to it cannot be coerced to numeric values. If converted to a numeric value, the result will be NA.
* Factor variable: The factor can be converted to numeric to calculate the mean.





